### 2020-04-22 survival.tex
chill

In addition to the strong {\em cage} and {\em node} hazard rate
differences that increase with distance from the bottom of the
cabines, seen in both KM and CPH results, there is a weaker but
peculiar pattern in the {\em row} and {\em col} hazard rates. The
different behavior in {\em col} 0-11 from {\em col} 12-24 is likely
due to separate supply lines of coolant to the two sets. But the
interleaving pattern of the first set is still a mystery. We also have
yet to explain the apparent row effects. A very minor
airflow effect across slots also seems to be present as it mimics
faster airflow for the middle slots.

>>>>

In addition to the strong {\em cage} and {\em node} hazard rate
differences that increase with distance from the bottom of the
cabines, seen in both KM and CPH results, there is a weaker but
peculiar pattern in the {\em row} and {\em col} hazard rates. The
different behavior in {\em col} 0-11 from {\em col} 12-24 is likely
due to separate supply lines of chilled water to the two sets. While
the temperature was a consistent 42$^\circ$F, there may have been
minor flow or pressure differences. But the interleaving pattern of
the first set is still a mystery. We also have yet to explain the
apparent row effects. A very minor airflow effect across slots also
seems to be present as it mimics faster airflow for the middle slots.
